Model to study co-evolution of trade an culture

### 2015-03-27 article.tex
work on the presentation of the setup

@@

\section{INTRODUCTION}

@@

\todo{find another title}
\subsection{Agent-based consumers and traders}
%tell the story of what is happening

The only mandatory elements are a set of agents each possessing a fixed number of goods and associate a value to each of these goods. The value can be for example either an interest in the good or the price associated to this good. The agents are also endowed with limited storage abilities for each good that can be produced.

@@

This scheme allow us to have a model achieving the two main goals listed in section~\ref{}. First, this model is flexible enough to allow the study of multiple hypothesis while conserving the same units that can therefore be compared between simulations. Second, few parameters are present in the model which makes it easier to analyse and reuse by other researchers.

\subsection{Experiment design}

In order to validate our model a first result from the literature on the evolutionary transmission is reproduced. We then tackle the inclusion of simple trade mechanisms in order to show the possibility to implement them and the possibility to compare the results obtained in both economy and cultural transmission.

\subsubsection{Cultural Evolution}

In our model the ``cultural change'' is represented by the variations in the distribution of prices for each good. In order to validate our model we will try two simple biases: simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009}. The aim is to show that these simple modifications can allow us to observe the emergence of different cultures, each modifying the price structure obtained. The price structure obtained will be also compare to the obtained by the the economical model explained at the previous section.

The production, consumption and trade phases described are not modified. However the price update phase is modified as follow. When the random copy behaviour is used each agent has a XXX\% chance to copy a new price from one agent selected randomly. Two frequency dependent behaviour are proposed. The first to be tested is the conformist behaviour with which each agent at each agent will have a XXXX\% chance to select the most common price for each good. The second to be tested is the rarity behaviour with which each agent at each iteration will have a XXX\% chance to select the least common beahviour.

\subsubsection{Economical Trading}\label{trade}

@@

@@

Finally, as mentioned before, each agent will consume a certain quantity of each good. This quantity can be a property of the agent, i.e. each agent consumes a different quantity of each product :
$$ consumption = (c^i_1, \cdots, c^i_n) $$

>>>>

\usepackage{mathtools}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%

\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother

@@

\section{INTRODUCTION}\label{sec:intro}

@@

In the model presented a set of agents are each in possession of a fixed number of goods and associate a value to each of these goods. Depending on the question studied, the value can reflect the interest of the agent for the good or it can be the price at which the agent evaluate this good. The agents are also endowed with limited storage abilities for each good that can be produced.

@@

On top of these elements two processes are included : imitation and innovation. The first one reflects the possibility for agents to imitate other agents. For this, an agent can copy the value vector of another agent. The second process reflects the possibility for an agent to associate new values for the goods. For this, an agent can select new elements for its value vector independently of the values of other agents.

This scheme allow us to have a model achieving the two main goals listed in section~\ref{sec:intro}. First, this model allows us to test various cultural transmission mechanisms as well as trade mechanisms. The experiments presented in this article show examples of implementations for both categories. Moreover, the fact that only two processes are modified allow comparisons between simulations with the same units. Second, few parameters are present in the default model which makes it easier to analyse and reuse by other researchers.

In order to validate our model a first result from the literature on the evolutionary transmission is reproduced. We then illustrate the possibility to implement a trade mechanisms.

\subsection{Cultural Transmission}

In this article the cultural transmission tested is the ``random copy" such as presented in~\cite{mesoudi_random_2009}. The aim is to show that our model is indeed able to reproduce the main trends expected with such copy mechanism. Namely, we should observe a distribution known as the power law, displaying a line in the log-log graph of the proportion of variants with regards to the frequency of variant.

The imitation process is a ``random copy" meaning that with a low probability each agent pick randomly one agent among all and copy it's vector of values. The innovation process is triggered with a low probability and select new elements for the vector of values. These new elements are drawn from a uniform distribution. The imitation and innovation probabilities are presented with other parameters in table~\ref{tab:parameters}

\subsection{Trading Model}\label{sec:trade}

\paragraph*{Imitation}
To test a simple trading model, two notions are introduced in the imitation mechanism: need and score. The need is a quantity of product that each agent tries to obtain. This quantity is different for each product but the need for a product is the same for all agents:
$$ need = (n_1, \cdots, n_r) $$

The score reflects the ability for an agent to obtain the products it needs, it is formally computed as follow for agent $i$:

$$ \abs{\dfrac{q^i_j - n_j}{ \sqrt{\abs{(q^i_j*q^i_j)-(n_j*n_j)}}}} $$

\paragraph*{Trading}

@@

\paragraph*{Innovation}

@@
